Assignment 1: Data and Descriptive

### 2023-10-12 MSB104_assignment1.qmd
Final commit of assignment 1, 12.10.23.

```{r}
#| echo: false
# Downloaded file for population in DE (Germany), FI (Finland) and RO (Romania). Furthermore, we load up the file i RStudio by import the file in Library(readr). Moreover, we commended RStudio to read the file "demo_r_pjanaggr3_page_linear_csv". Additionally, we implemented the function na = "NA" for RStudio to read the missing values. Lastly, we added the function "show_col_types = FALSE" to prevent RStudio displaying the column data types while reading the file. 
library(readr)
demo_r_pjanaggr3_page_linear_csv <- read_csv("demo_r_pjanaggr3_page_linear.csv.gz", 
    na = "NA", show_col_types = FALSE)
```

```{r}
#| echo: false
# First step was to rename the file for the assigned countries (DE, FI & RO). Furthermore, we utilized the function filter with str_sub considering a better overview of relevant dataset. Lastly, we were interested in population in every sub_regionals in the relevant contries. To receive and organise the relevant data, the function "Select" was used.  
DE_FI_RO_pop <- demo_r_pjanaggr3_page_linear_csv |>
	filter(str_sub
	       (geo, start = 1L, end = 2L) %in% c("DE", "FI", "RO")) |>
	select(Year = TIME_PERIOD, Sub_regions = geo, Population = OBS_VALUE)
```

@@

```{r}
#| echo: false
# Downloaded file for GDP in DE (Germany), FI (Finland) and RO (Romania). Furthermore, we load up the file i RStudio by import the file in Library(readr). Moreover, we commended RStudio to read the file "nama_10r_3gdp_page_linear_csv". Additionally, we implemented the function na = "NA" for RStudio to read the missing values. Lastly, we added the function "show_col_types = FALSE" to prevent RStudio displaying the column data types while reading the file. 
library(readr)
nama_10r_3gdp_page_linear_csv <- read_csv("nama_10r_3gdp_page_linear.csv.gz", 
    na = "NA", show_col_types = FALSE)
```

```{r}
#| echo: false
# First step was to rename the file for the assigned countries (DE, FI & RO). Furthermore, we utilized the function filter with str_sub considering a better overview of relevant dataset. Lastly, we were interested in population in every sub_regionals in the relevant contries. To receive and organise the relevant data, the function "Select" was used.  
DE_FI_RO_gdp <- nama_10r_3gdp_page_linear_csv |>
	filter(str_sub
	       (geo, start = 1L, end = 2L) %in% c("DE", "FI", "RO")) |>
	select(Year = TIME_PERIOD, Sub_regions = geo, GDP = OBS_VALUE)
```

@@

```{r}
#| echo: false
#| warning: false
# Created new dataset called GDP_DE_nuts2.
# Filtered sub-regions from Germany by using str_sub to extract a substring from the Sub_regions columns containing the letters DE for Germany.
# Creating new column called id_nuts2 to save the new data for calculating Gini coefficient, for presenting the numbers of regional inequity in Germany at NUTS2 level.
# Next step is to group the numbers of NUTS2 level sorted by the the code of the region in NUTS2 level and year.
# Finally summarise the Gini coefficient numbers of each German region in NUTS2 level by multiplying 1 000 000 with GDP divided by population. 
GDP_DE_nuts2 <- merged_data %>%
  filter(
    str_sub(Sub_regions, start = 1L, end = 2L) == "DE"
  ) |> 
  mutate(
    id_nuts2 = fct(str_sub(Sub_regions, start = 1L, end = 4L))
  ) |> 
  group_by(id_nuts2, Year) %>%
  summarise(
    GDP_per_capita_nuts2_DE = sum(1000000*GDP)/sum(Population)
    ) 
```

@@

```{r}
#| label: fig-regional_gdp_per_year_NG
#| echo: false
#| cap-location: bottom
#| fig-cap: "GDP per capita in year - Northern Germany"
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_DE_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_DE_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we use geom_line since this gives a accurate description of our data from Germany.
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz1NORTH
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  geom_line()
```

```{r}
#| label: fig-regional_gdp_per_year_SG
#| echo: false
#| #| cap-location: bottom
#| fig-cap: "GDP per capita in year - Southern Germany"
# Duplicating the same steps for Southern Germany as for the Northern part. 
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz2SOUTH
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  geom_line()
```

@@

```{r}
#| echo: false
#| warning: false
# Created new dataset called GDP_FI_nuts2.
# Filtered sub-regions from Finland by using str_sub to extract a substring from the Sub_regions columns containing the letters FI for Finland
# Creating new column called id_nuts2 to save the new data for calculating Gini coefficient, for presenting the numbers of regional inequity in Finland at NUTS2 level.
# Next step is to group the numbers of NUTS2 level sorted by the the code of the region in NUTS2 level and year.
# Finally summarise the Gini coefficient numbers of each Finnish region in NUTS2 level by multiplying 1 000 000 with GDP divided by population. 
GDP_FI_nuts2 <- merged_data %>%
  filter(
    str_sub(Sub_regions, start = 1L, end = 2L) == "FI"
  ) |> 
  mutate(
    id_nuts2 = fct(str_sub(Sub_regions, start = 1L, end = 4L))
  ) |> 
  group_by(id_nuts2, Year) %>%
  summarise(
    GDP_per_capita_nuts2_FI = sum(1000000*GDP)/sum(Population)
    ) 
```

```{r}
#| label: fig-regional_gdp_per_year_FI
#| echo: false
#| #| cap-location: bottom
#| fig-cap: "GDP per capita in year - Finland"
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_FI_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_FI_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we use geom_line since this gives a accurate description of our data from Finland
GDP_FI_nuts2 |>
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_FI, 
    colour = id_nuts2)
    ) +
  geom_line()
```

@@

```{r}
#| echo: false
#| warning: false
# Created new dataset called GDP_RO_nuts2.
# Filtered sub-regions from Romania by using str_sub to extract a substring from the Sub_regions columns containing the letters RO for Romania
# Creating new column called id_nuts2 to save the new data for calculating Gini coefficient, for presenting the numbers of regional inequity in Romania at NUTS2 level.
# Next step is to group the numbers of NUTS2 level sorted by the the code of the region in NUTS2 level and year.
# Finally summarise the Gini coefficient numbers of each Romanian region in NUTS2 level by multiplying 1 000 000 with GDP divided by population. 
GDP_RO_nuts2 <- merged_data %>%
  filter(
    str_sub(Sub_regions, start = 1L, end = 2L) == "RO"
  ) |> 
  mutate(
    id_nuts2 = fct(str_sub(Sub_regions, start = 1L, end = 4L))
  ) |> 
  group_by(id_nuts2, Year) %>%
  summarise(
    GDP_per_capita_nuts2_RO = sum(1000000*GDP)/sum(Population)
    ) 
```

```{r}
#| label: fig-regional_gdp_per_year_RO
#| echo: false
#| #| cap-location: bottom
#| fig-cap: "GDP per capita in year - Romania"
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_RO_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_RO_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we use geom_line since this gives a accurate description of our data from Romania
GDP_RO_nuts2 |>
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_RO, 
    colour = id_nuts2)
    ) +
  geom_line()
```

@@

```{r}
#| echo: false
# Firstly, we create a new dataset called Gini_stat_DE_nuts2. 
# Secondly, we filter the data to include only rows where the id_nuts2 variable is in the DE group. 
# Thirdyly, after filtering, the data is grouped by the Year variable. This means that subsequent calculations will be performed separately for each year.
# Lastly, we use summarise to calculates summary statistics for the gini_n2 variable within each group (each year). 
Gini_stat_DE_nuts2 <- merged_temp %>%
  filter(id_nuts2 %in% DE) |> 
  group_by(Year) |> 
  summarise(
    min = min(gini_n2),
    max = max(gini_n2),
    median = median(gini_n2),
    mean = mean(gini_n2),
    sd = sd(gini_n2),
    var = sd^2
  )
```

@@

```{r}
#| echo: false
# Firstly, we create a new dataset called Gini_stat_FI_nuts2. 
# Secondly, we filter the data to include only rows where the id_nuts2 variable is in the FI group. 
# Thirdyly, after filtering, the data is grouped by the Year variable. This means that subsequent calculations will be performed separately for each year.
# Lastly, we use summarise to calculates summary statistics for the gini_n2 variable within each group (each year).
Gini_stat_FI_nuts2 <- merged_temp %>%
  filter(id_nuts2 %in% FI) |> 
  group_by(Year) |> 
  summarise(
    min = min(gini_n2),
    max = max(gini_n2),
    median = median(gini_n2),
    mean = mean(gini_n2),
    sd = sd(gini_n2),
    var = sd^2
  )
```

@@

```{r}
#| echo: false
# Firstly, we create a new dataset called Gini_stat_RO_nuts2. 
# Secondly, we filter the data to include only rows where the id_nuts2 variable is in the RO group. 
# Thirdyly, after filtering, the data is grouped by the Year variable. This means that subsequent calculations will be performed separately for each year.
# Lastly, we use summarise to calculates summary statistics for the gini_n2 variable within each group (each year).
Gini_stat_RO_nuts2 <- merged_temp %>%
  filter(id_nuts2 %in% RO) |> 
  group_by(Year) |> 
  summarise(
    min = min(gini_n2),
    max = max(gini_n2),
    median = median(gini_n2),
    mean = mean(gini_n2),
    sd = sd(gini_n2),
    var = sd^2
  )
```

>>>>

```{r}
#| echo: false
# Downloaded file for population in DE (Germany), FI (Finland) and RO (Romania). Furthermore, we load up the file i RStudio by import the file in Library(readr). Moreover, we commended RStudio to read the file "demo_r_pjanaggr3_page_linear_csv". Additionally, we implement the function na = "NA" for RStudio to read the missing values. Lastly, we add the function "show_col_types = FALSE" to prevent RStudio displaying the column data types while reading the file. 
library(readr)
demo_r_pjanaggr3_page_linear_csv <- read_csv("demo_r_pjanaggr3_page_linear.csv.gz", 
    na = "NA", show_col_types = FALSE)
```

```{r}
#| echo: false
# First step is to rename the file for the assigned countries (DE, FI & RO). Furthermore, we utilize the function filter with str_sub considering a better overview of relevant dataset. Lastly, we are interested in population in every sub_regionals in the relevant contries. To receive and organise the relevant data, the function "Select" is used.  
DE_FI_RO_pop <- demo_r_pjanaggr3_page_linear_csv |>
	filter(str_sub
	       (geo, start = 1L, end = 2L) %in% c("DE", "FI", "RO")) |>
	select(Year = TIME_PERIOD, Sub_regions = geo, Population = OBS_VALUE)
```

@@

```{r}
#| echo: false
# Download file for GDP in DE (Germany), FI (Finland) and RO (Romania). Furthermore, we load up the file i RStudio by import the file in Library(readr). Moreover, we commend RStudio to read the file "nama_10r_3gdp_page_linear_csv". Additionally, we implement the function na = "NA" for RStudio to read the missing values. Lastly, we add the function "show_col_types = FALSE" to prevent RStudio displaying the column data types while reading the file. 
library(readr)
nama_10r_3gdp_page_linear_csv <- read_csv("nama_10r_3gdp_page_linear.csv.gz", 
    na = "NA", show_col_types = FALSE)
```

```{r}
#| echo: false
# First step is to rename the file for the assigned countries (DE, FI & RO). Furthermore, we utilize the function filter with str_sub considering a better overview of relevant dataset. Lastly, we are interested in population in every sub_regionals in the relevant contries. To receive and organise the relevant data, the function "Select" is used.  
DE_FI_RO_gdp <- nama_10r_3gdp_page_linear_csv |>
	filter(str_sub
	       (geo, start = 1L, end = 2L) %in% c("DE", "FI", "RO")) |>
	select(Year = TIME_PERIOD, Sub_regions = geo, GDP = OBS_VALUE)
```

@@

```{r}
#| echo: false
#| warning: false
# Create new dataset called GDP_DE_nuts2.
# Filter sub-regions from Germany by using str_sub to extract a substring from the Sub_regions columns containing the letters DE for Germany.
# Creating new column called id_nuts2 to save the new data for calculating Gini coefficient, for presenting the numbers of regional inequity in Germany at NUTS2 level.
# Next step is to group the numbers of NUTS2 level sorted by the the code of the region in NUTS2 level and year.
# Finally summarise the Gini coefficient numbers of each German region in NUTS2 level by multiplying 1 000 000 with GDP divided by population. 
GDP_DE_nuts2 <- merged_data %>%
  filter(
    str_sub(Sub_regions, start = 1L, end = 2L) == "DE"
  ) |> 
  mutate(
    id_nuts2 = fct(str_sub(Sub_regions, start = 1L, end = 4L))
  ) |> 
  group_by(id_nuts2, Year) %>%
  summarise(
    GDP_per_capita_nuts2_DE = sum(1000000*GDP)/sum(Population)
    ) 
```

@@

```{r}
#| label: fig-regional_gdp_per_year_NG
#| echo: false
#| cap-location: bottom
#| fig-cap: "GDP per capita in year - Northern Germany"
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_DE_nuts2 to contain the values in Northern Germany (DEz1NORTH) from column id_nuts2.
# Thirdly, we represent the data in GPD_DE_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we use geom_line since this gives a accurate description of our data from Germany.
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz1NORTH
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  geom_line()
```

```{r}
#| label: fig-regional_gdp_per_year_SG
#| echo: false
#| #| cap-location: bottom
#| fig-cap: "GDP per capita in year - Southern Germany"
# Duplicating the same steps for Southern Germany (DEz2SOUTH) as for the Northern part. 
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz2SOUTH
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  geom_line()
```

@@

```{r}
#| echo: false
#| warning: false
# Create new dataset called GDP_FI_nuts2.
# Filter sub-regions from Finland by using str_sub to extract a substring from the Sub_regions columns containing the letters FI for Finland.
# Creating new column called id_nuts2 to save the new data for calculating Gini coefficient, for presenting the numbers of regional inequity in Finland at NUTS2 level.
# Next step is to group the numbers of NUTS2 level sorted by the the code of the region in NUTS2 level and year.
# Finally summarise the Gini coefficient numbers of each Finnish region in NUTS2 level by multiplying 1 000 000 with GDP divided by population. 
GDP_FI_nuts2 <- merged_data %>%
  filter(
    str_sub(Sub_regions, start = 1L, end = 2L) == "FI"
  ) |> 
  mutate(
    id_nuts2 = fct(str_sub(Sub_regions, start = 1L, end = 4L))
  ) |> 
  group_by(id_nuts2, Year) %>%
  summarise(
    GDP_per_capita_nuts2_FI = sum(1000000*GDP)/sum(Population)
    ) 
```

```{r}
#| label: fig-regional_gdp_per_year_FI
#| echo: false
#| #| cap-location: bottom
#| fig-cap: "GDP per capita in year - Finland"
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_FI_nuts2 to contain the regions in Finland from column id_nuts2.
# Thirdly, we represent the data in GPD_FI_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we use geom_line since this gives a accurate description of our data from Finland
GDP_FI_nuts2 |>
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_FI, 
    colour = id_nuts2)
    ) +
  geom_line()
```

@@

```{r}
#| echo: false
#| warning: false
# Create new dataset called GDP_RO_nuts2.
# Filter sub-regions from Romania by using str_sub to extract a substring from the Sub_regions columns containing the letters RO for Romania
# Creating new column called id_nuts2 to save the new data for calculating Gini coefficient, for presenting the numbers of regional inequity in Romania at NUTS2 level.
# Next step is to group the numbers of NUTS2 level sorted by the the code of the region in NUTS2 level and year.
# Finally summarise the Gini coefficient numbers of each Romanian region in NUTS2 level by multiplying 1 000 000 with GDP divided by population. 
GDP_RO_nuts2 <- merged_data %>%
  filter(
    str_sub(Sub_regions, start = 1L, end = 2L) == "RO"
  ) |> 
  mutate(
    id_nuts2 = fct(str_sub(Sub_regions, start = 1L, end = 4L))
  ) |> 
  group_by(id_nuts2, Year) %>%
  summarise(
    GDP_per_capita_nuts2_RO = sum(1000000*GDP)/sum(Population)
    ) 
```

```{r}
#| label: fig-regional_gdp_per_year_RO
#| echo: false
#| #| cap-location: bottom
#| fig-cap: "GDP per capita in year - Romania"
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_RO_nuts2 to contain the regions in Romania from column id_nuts2.
# Thirdly, we represent the data in GPD_RO_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we use geom_line since this gives a accurate description of our data from Romania
GDP_RO_nuts2 |>
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_RO, 
    colour = id_nuts2)
    ) +
  geom_line()
```

@@

```{r}
#| echo: false
# Firstly, we create a new dataset called Gini_stat_DE_nuts2. 
# Secondly, we filter the data to include only rows where the id_nuts2 variable is in the DE group. 
# Thirdly, after filtering, the data is grouped by the Year variable. This means that subsequent calculations will be performed separately for each year.
# Lastly, we use summarise to calculates summary statistics for the gini_n2 variable within each group (each year). 
Gini_stat_DE_nuts2 <- merged_temp %>%
  filter(id_nuts2 %in% DE) |> 
  group_by(Year) |> 
  summarise(
    min = min(gini_n2),
    max = max(gini_n2),
    median = median(gini_n2),
    mean = mean(gini_n2),
    sd = sd(gini_n2),
    var = sd^2
  )
```

@@

```{r}
#| echo: false
# Firstly, we create a new dataset called Gini_stat_FI_nuts2. 
# Secondly, we filter the data to include only rows where the id_nuts2 variable is in the FI group. 
# Thirdly, after filtering, the data is grouped by the Year variable. This means that subsequent calculations will be performed separately for each year.
# Lastly, we use summarise to calculates summary statistics for the gini_n2 variable within each group (each year).
Gini_stat_FI_nuts2 <- merged_temp %>%
  filter(id_nuts2 %in% FI) |> 
  group_by(Year) |> 
  summarise(
    min = min(gini_n2),
    max = max(gini_n2),
    median = median(gini_n2),
    mean = mean(gini_n2),
    sd = sd(gini_n2),
    var = sd^2
  )
```

@@

```{r}
#| echo: false
# Firstly, we create a new dataset called Gini_stat_RO_nuts2. 
# Secondly, we filter the data to include only rows where the id_nuts2 variable is in the RO group. 
# Thirdly, after filtering, the data is grouped by the Year variable. This means that subsequent calculations will be performed separately for each year.
# Lastly, we use summarise to calculates summary statistics for the gini_n2 variable within each group (each year).
Gini_stat_RO_nuts2 <- merged_temp %>%
  filter(id_nuts2 %in% RO) |> 
  group_by(Year) |> 
  summarise(
    min = min(gini_n2),
    max = max(gini_n2),
    median = median(gini_n2),
    mean = mean(gini_n2),
    sd = sd(gini_n2),
    var = sd^2
  )
```
